---
title: "Running RothC in Real Time at L'lara"
author: "Kate Coelli"
date: "4/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparing the information required by the model

### Required libraries 
```{r libraries, message = FALSE, warning = FALSE}
library(SoilR)
library(tidyverse)
library(knitr)
```

### Required functions
Sabastine's RothC functions
```{r functions}

source("../../../../Useful_functions/Sabastines_RothC_functions/RothC_functions.R")

```

### Required data
Before this code can be run, the required data must be obtained and tidied
This data has some overlap with the data required to run the model in equilibrium mode, and some differences
* The soil data is the same as the equilibrium run
* The monthly data is in real time, rather than long term averages
* Equilibrium mode needs to be run to determine the optimised starting pools of carbon

```{r data tidying, eval = FALSE}
#Run this first
file.edit("Running RothC in Equilibrium Mode.Rmd")

#followed by this
file.edit("RealTime_monthly_data.R")

```

If these files have already been executed, load in the relevant outputs

```{r data, echo = FALSE}
soil_data<- read.csv("../Processed_Data/soil_data_RT.csv") #This includes the SOC fractions derived in the equilibrium run
Monthly_climate<- read.csv("../Processed_Data/LTA_climate_data.csv")
kable(soil_data, caption = "Soil Data")
kable(LTA_climate, caption ="Long term average climate data")
```